Refinement for open automata

### 2021-05-15 2021-Refinement/Traffic_Lights_Spec.tex
Checked up to section 5

\draw (v1) edge[dir=220] node[below] {\OTd{\act{tick}}{cnt \mapsto \act{tick}}{}} (v1);
\draw (v1) edge[dir=150] node[left] {\OTd{\act{onRed}}{}{}} (v1);
\draw (v1) edge[dir=80] node[above] {\OTd{\tau}{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}{}} (v1);
\draw (v1) edge node {\OTd{\act{TurnGreen}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v2);
\draw (v2) edge[dir=100] node[above] {\OTd{\act{tick}}{cnt \mapsto \act{tick}}{}} (v2);
\draw (v2) edge[dir=30] node[right] {\OTd{\act{onGreen}}{}{}} (v2);
\draw (v2) edge[dir=320] node[xshift=1cm,below] {\OTd{\tau}{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}{}} (v2);
\draw (v2) edge node[pos=0.6] {\OTd{\act{TurnYellow}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v3);
\draw (v3) edge[dir=340] node {\OTd{\act{tick}}{cnt \mapsto \act{tick}}{}} (v3);
\draw (v3) edge[dir=270] node {\OTd{\act{onYellow}}{}{}} (v3);
\draw (v3) edge[dir=200] node {\OTd{\tau}{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}{}} (v3);
\draw (v3) edge node[pos=0.4] {\OTd{\act{TurnRed}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v1);

>>>>

\draw (v1) edge[dir=220] node[below] {\OTd{\act{tick}}{cnt \mapsto \act{tick}}{}} (v1);
\draw (v1) edge[dir=150] node[left] {\OTd{\act{onRed}}{}{}} (v1);
\draw (v1) edge[dir=80] node[above] {\OTd{\tau}{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}{}} (v1);
\draw (v1) edge node {\OTd{\act{TurnGreen}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v2);
\draw (v2) edge[dir=100] node[above] {\OTd{\act{tick}}{cnt \mapsto \act{tick}}{}} (v2);
\draw (v2) edge[dir=30] node[right] {\OTd{\act{onGreen}}{}{}} (v2);
\draw (v2) edge[dir=320] node[xshift=1cm,below] {\OTd{\tau}{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}{}} (v2);
\draw (v2) edge node[pos=0.6] {\OTd{\act{TurnYellow}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v3);
\draw (v3) edge[dir=340] node {\OTd{\act{tick}}{cnt \mapsto \act{tick}}{}} (v3);
\draw (v3) edge[dir=270] node {\OTd{\act{onYellow}}{}{}} (v3);
\draw (v3) edge[dir=200] node {\OTd{\tau}{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}{}} (v3);
\draw (v3) edge node[pos=0.4] {\OTd{\act{TurnRed}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v1);
